Astrophysical calibration of gravitational-wave detectors

### 2015-07-03 docs/cosmic_cal.tex
Minor updated to draft

Finally, we require a prior on the calibration scale factors for each detector. We make the 
assumption that in general the calibration will be correct, so want to use a prior that is peaked 
at unity. We also assume that the probability density that the calibration scale factor is either 
larger or smaller than unity by an equivalent factor, e.g.\ $s=10$ or $s=0.1$, is the same. For this 
we therefore use a log-normal distribution as our prior
\begin{equation}
 p(s|I) = \frac{1}{s\sigma\sqrt{2\pi}}\exp{\left( -\frac{(\ln{s} - \mu)^2}{2\sigma^2} \right)},
\end{equation}
where we chose $\sigma = 1$, which in turn means that having the mode at unity gives $\mu = 1$. 
With these parameters the prior probability density at 0.1 and 10 is $\sim 1/14$ of that at 1. 
Note that this prior does not provide produce a symmetric amount of probability about unity, but 
given our simulation criterion described below in Section~\ref{sec:simulations} we find that the 
likelihood generally overwhelms the prior. As $s$ is a scale factor we also have the further 
constraint that it must be positive.

@@

For each source we applied a fixed calibration scale factor of 1.2, 0.8 and 1.3 for H1, L1 and V1 
respectively.

>>>>

Finally, we require a prior on the calibration scale factors for each detector. We make the 
assumption that in general the calibration will be correct, so want to use a prior that is peaked 
at unity. We also assume that the probability density that the calibration scale factor is either 
larger or smaller than unity by an equivalent factor, e.g.\ $s=10$ or $s=0.1$, is the same. For this 
we therefore use a log-normal distribution as our prior
\begin{equation}
 p(s|I) = \frac{1}{s\sigma\sqrt{2\pi}}\exp{\left( -\frac{(\ln{s} - \mu)^2}{2\sigma^2} \right)},
\end{equation}
where we chose $\sigma = 1.07$, which in turn means that having the mode at unity gives $\mu = 
1.15$. With these parameters the prior probability density at 0.1 and 10 is one tenth of that at 
1. Note that this prior does not provide produce a symmetric amount of probability about unity, but 
given our simulation criterion described below in Section~\ref{sec:simulations} we find that the 
likelihood generally overwhelms the prior. As $s$ is a scale factor we also have the further 
constraint that it must be positive.

@@

For each simulation the calibration scale factor for each detector has been drawn from a Gaussian 
distribution with a mean of unity and a standard deviation of 0.125 (equivalent to the detectors 
having on average a $\pm 10\%$ amplitude calibration error).
